---
title: "Alcohol vs Seat choice"
author: "Xavier Cruz"
date: "Spring 2025" 
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

```{r include=FALSE}
require(tidyverse)
require(tigerstats)
davisdata <- read.csv(file="UCDavis.csv")
```
## Our Goal is to answer this question Is there a difference between the alcohol consumed between the row
## you choose to sit in??

## Now with ggplot - first select the basic data

```{r}
basicCN <- ggplot(ucdavis1,aes(x=Seat,y=alcohol))
```
## Now add in boxplot

```{r}
boxplot(alcohol~Seat,data=davisdata)
```

  The boxes are not disjoint. In the boxplot, the median of the back box is higher then that of the front and middle boxes. The front and middle boxes exhibit similar sizes, though the middle box contains a higher number of outliers compared to the front box.
  
### get fancy  

```{r}
basicCN + geom_boxplot(notch=TRUE,outlier.color = "red") + stat_boxplot(geom ='errorbar') + labs(title="Fancy notch boxplot \n with 2 lines")
```

## Numerical Summarys 

```{r}
favstats(alcohol~Seat,data=ucdavis1)
```

The back seat shows the highest values and most variability, with a median of 3.5 and a mean of 8.56. The middle seat data is intermediate with a median of 1 and a mean 3.33. The front seat data has the smallest values and least variability, with a median of 0 and a mean of 1.79.
## Inferential Tests

## Conclusions


