---
title: "Alcohol vs Seat choice"
author: "Xavier Cruz"
date: "Spring 2025" 
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

```{r include=FALSE}
require(tidyverse)
require(tigerstats)
davisdata <- read.csv(file="UCDavis.csv")
```
## Our Goal is to answer this question Is there a difference between the alcohol consumed between the row
## you choose to sit in??

## Now with ggplot - first select the basic data

```{r}
basicCN <- ggplot(ucdavis1,aes(x=Seat,y=alcohol))
```
## Now add in boxplot

```{r}
boxplot(alcohol~Seat,data=davisdata)
```

  The boxes are not disjoint. In the boxplot, the median of the back box is higher then that of the front and middle boxes. The front and middle boxes exhibit similar sizes, though the middle box contains a higher number of outliers compared to the front box.
  
### get fancy  

```{r}
basicCN + geom_boxplot(notch=TRUE,outlier.color = "red") + stat_boxplot(geom ='errorbar') + labs(title="Fancy notch boxplot \n with 2 lines")
```

## Numerical Summarys 

```{r}
favstats(alcohol~Seat,data=ucdavis1)
```

The back seat shows the highest values and most variability, with a median of 3.5 and a mean of 8.56. The middle seat data is intermediate with a median of 1 and a mean 3.33. The front seat data has the smallest values and least variability, with a median of 0 and a mean of 1.79.

## Inferential Tests

```{r}
model1 <- aov(alcohol~Seat,data=davisdata)
summary.aov(model1)
```

The probability of obtaining these results is one of ten thousand. Further analysis is required to determine which sets differ from one another.

## Conclusions

I created a box plot to visually represent the consumption across different rows, highlighting the difference in consumption levels. The numerical summery revealed that the back row consumed twice as much alcohol compared to the other rows. When comparing three or more groups, a one way ANOVA is used to determine if there are significant differences among these. If the ANOVA test yields a p value between 0 and 1, further investigation is needed, which may involve additional analyses and plotted a revised  model that highlighted the distinct contrast in alcohol consumption in the back.


